---
title: "DSN 2019 Cross Sections"
author: "Daniel"
date: "November 29, 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading data and libraries

Load ggplot2 for plotting data and the CSV file with all data. We also correct the cross section of thermals since the rotax spectrum is different, which means we should correct the fluence we had before by a factor of (4.96/2.71). Thus, we divide the cross section by this factor since the cross section is (number of errors)/(fluence).

```{r}
library(ggplot2)
library(reshape2)

dat = read.csv("data_formatted.csv",sep=",")

dat$cross_section_SDC_thermals = dat$cross_section_SDC_thermals / (4.96/2.71)

summary(dat)
```


## Normalize SDC and DUE Cross Sections

Find the minimum value for each device and normalize SDC and DUE cross sections. Then, append the values normalize to a new data frame called "datNormalized"

```{r}
datNormalized = dat
for (board in unique(dat$Device)) {
  # Get all cross section values for one device
  tmp_values = c(subset(dat,dat$Device==board)$cross_section_SDC_high, subset(dat,dat$Device==board)$cross_section_DUE_high, subset(dat,dat$Device==board)$cross_section_SDC_thermals, subset(dat,dat$Device==board)$cross_section_DUE_thermals)
  tmp_values = tmp_values[tmp_values > 0] # remove zeros in case there is zeros
  tmp_min = min(tmp_values, na.rm=TRUE) # get the minimum cross section value
  print(paste("Device: ", board, "; Minimum: ",tmp_min))
  
  # Normalize all date from one device to the minimum value found
  datNormalized[datNormalized$Device == board, ]$cross_section_SDC_high = datNormalized[datNormalized$Device == board, ]$cross_section_SDC_high / tmp_min
  datNormalized[datNormalized$Device == board, ]$cross_section_DUE_high = datNormalized[datNormalized$Device == board, ]$cross_section_DUE_high / tmp_min
  datNormalized[datNormalized$Device == board, ]$cross_section_SDC_thermals = datNormalized[datNormalized$Device == board, ]$cross_section_SDC_thermals / tmp_min
  datNormalized[datNormalized$Device == board, ]$cross_section_DUE_thermals = datNormalized[datNormalized$Device == board, ]$cross_section_DUE_thermals / tmp_min
}
```


## Compute FIT for High Energy

Normal flux is 13 neutrons per cm^2 per hour. Since data is normalized, there is no need to multiply by 10^9

```{r}
datNormalized$FIT_SDC_high = datNormalized$cross_section_SDC_high * 13
datNormalized$FIT_DUE_high = datNormalized$cross_section_DUE_high * 13
```

## Compute FIT for Thermals


Normal flux is 4 neutrons per cm^2 per hour under normal environments. 

```{r}
datNormalized$FIT_SDC_thermals = datNormalized$cross_section_SDC_thermals * 4
datNormalized$FIT_DUE_thermals = datNormalized$cross_section_DUE_thermals * 4
```

During a thunderstrom the neutron flux is about 8 neutrons

```{r}
datNormalized$FIT_SDC_thermals_storm = datNormalized$cross_section_SDC_thermals * 8
datNormalized$FIT_DUE_thermals_storm = datNormalized$cross_section_DUE_thermals * 8
```

## Compute the error bars

Using the Poisson distribution with 95% confidence, which is  1.96*sqrt(test_mean/#tests)

```{r}
  datNormalized$cross_section_SDC_high_err = 1.96*sqrt(datNormalized$cross_section_SDC_high/datNormalized$number_SDCs_high)
  datNormalized$cross_section_DUE_high_err = 1.96*sqrt(datNormalized$cross_section_DUE_high/datNormalized$number_DUE_high)

  datNormalized$cross_section_SDC_thermals_err = 1.96*sqrt(datNormalized$cross_section_SDC_thermals/datNormalized$number_SDCs_thermals)
  datNormalized$cross_section_DUE_thermals_err = 1.96*sqrt(datNormalized$cross_section_DUE_thermals/datNormalized$number_DUE_thermals)
  
  datNormalized$FIT_SDC_high_err = 1.96*sqrt(datNormalized$FIT_SDC_high/datNormalized$number_SDCs_high)
  datNormalized$FIT_DUE_high_err = 1.96*sqrt(datNormalized$FIT_DUE_high/datNormalized$number_DUE_high)

  datNormalized$FIT_DUE_thermals_err = 1.96*sqrt(datNormalized$FIT_DUE_thermals/datNormalized$number_DUE_thermals)
  datNormalized$FIT_SDC_thermals_err = 1.96*sqrt(datNormalized$FIT_SDC_thermals/datNormalized$number_SDCs_thermals)

  datNormalized$FIT_SDC_thermals_storm_err = 1.96*sqrt(datNormalized$FIT_SDC_thermals_storm/datNormalized$number_SDCs_thermals)
  datNormalized$FIT_DUE_thermals_storm_err = 1.96*sqrt(datNormalized$FIT_DUE_thermals_storm/datNormalized$number_DUE_thermals)
```



## Cross Sections Plots


### AMD

```{r}
  datPlot = subset(datNormalized, Device=="CPU" | Device == "GPUembedded" | Device == "CPU+GPU")
  
  dfm1 = melt(datPlot[, c('Code', 'Device', 'cross_section_SDC_high_err', 'cross_section_SDC_high')], id.vars = c(1, 2, 3))
  colnames(dfm1) = c("Code", "Device", "Error", "Neutron_Type", "Cross_Section")
  dfm1$Neutron_Type = "High Energy (SDC)"
  dfm1$Event_Type = "SDC"
  colnames(dfm1) = c("Code", "Device", "Error", "Neutron_Type", "Cross_Section", "Event_Type")
  
  dfm2 = melt(datPlot[, c('Code', 'Device', 'cross_section_SDC_thermals_err', 'cross_section_SDC_thermals')], id.vars = c(1, 2, 3))
  colnames(dfm2) = c("Code", "Device", "Error", "Neutron_Type", "Cross_Section")
  dfm2$Neutron_Type = "Thermals (SDC)"
  dfm2$Event_Type = "SDC"
  colnames(dfm2) = c("Code", "Device", "Error", "Neutron_Type", "Cross_Section", "Event_Type")
  
  dfm3 = melt(datPlot[, c('Code', 'Device', 'cross_section_DUE_high_err', 'cross_section_DUE_high')], id.vars = c(1, 2, 3))
  colnames(dfm3) = c("Code", "Device", "Error", "Neutron_Type", "Cross_Section")
  dfm3$Neutron_Type = "High Energy (DUE)"
  dfm3$Event_Type = "DUE"
  colnames(dfm3) = c("Code", "Device", "Error", "Neutron_Type", "Cross_Section", "Event_Type")
  
  dfm4 = melt(datPlot[, c('Code', 'Device', 'cross_section_DUE_thermals_err', 'cross_section_DUE_thermals')], id.vars = c(1, 2, 3))
  colnames(dfm4) = c("Code", "Device", "Error", "Neutron_Type", "Cross_Section")
  dfm4$Neutron_Type = "Thermals (DUE)"
  dfm4$Event_Type = "DUE"
  colnames(dfm4) = c("Code", "Device", "Error", "Neutron_Type", "Cross_Section", "Event_Type")
  
  dfm = rbind(dfm1, dfm2, dfm3, dfm4)
  
  
  dfm[2] <- data.frame(lapply(dfm[2], function(x) { gsub("GPUembedded", "AMD\nGPU", x) }))
  dfm[2] <- data.frame(lapply(dfm[2], function(x) { gsub("CPU", "AMD\nCPU", x) }))
  dfm[2] <- data.frame(lapply(dfm[2], function(x) { gsub("CPU+GPU", "AMD\nCPU+GPU", x) }))
  
  dfm$Device <- factor(dfm$Device, levels = c("AMD\nCPU", "AMD\nGPU", "AMD\nCPU+GPU"))
  dfm$Neutron_Type <- factor(dfm$Neutron_Type, levels = c("High Energy (SDC)", "Thermals (SDC)", "High Energy (DUE)", "Thermals (DUE)"))
  
  plot = ggplot(dfm, aes(x=Code, weight=Cross_Section, ymin=Cross_Section-Error, ymax=Cross_Section+Error, fill=Neutron_Type, colour=Neutron_Type)) +
  geom_bar      (position=position_dodge(), aes(y=Cross_Section), stat="identity") +
  geom_errorbar (position=position_dodge(width=0.9), width=0.2, colour="black") +
    facet_grid(~ Device) +
  labs(x = "", y = "Cross Section [a.u.]", fill="", color="") +
    scale_color_manual(values = c("red", "black", "red", "black")) +
    scale_fill_manual(values=c("#1f78b4", "#33a02c", "#a6cee3", "#b2df8a")) + #, labels=c("Thermals (DUE)" = "", "Thermals (SDC)" = "Thermals", "High Energy (DUE)" = "", "High Energy (SDC)" = "High Energy")) +
    #scale_color_manual(values=c("#999999", "#000000")) +
    #scale_fill_manual(values=c("#990000", "#009F00", "#990000", "#009F00")) +
    #guides(color=guide_legend(nrow = 2)) +
    theme(legend.position="bottom")
  #theme(legend.position="bottom",axis.text.x=element_text(size=14) , axis.text.y=element_text(size=14) , text = element_text(size = 14))
  #filename = paste("./plots/FIT_SDC_", device, ".pdf", sep="")
  ggsave("./plots_final/cs_SDC_DUE_APU.pdf", plot, width = 12, height = 4)
  plot
```

### NVIDIA

```{r}
  datPlot = subset(datNormalized, Device=="K20" | Device == "TitanV" | Device == "TitanX")
  
  dfm1 = melt(datPlot[, c('Code', 'Device', 'cross_section_SDC_high_err', 'cross_section_SDC_high')], id.vars = c(1, 2, 3))
  colnames(dfm1) = c("Code", "Device", "Error", "Neutron_Type", "Cross_Section")
  dfm1$Neutron_Type = "High Energy (SDC)"
  dfm1$Event_Type = "SDC"
  colnames(dfm1) = c("Code", "Device", "Error", "Neutron_Type", "Cross_Section", "Event_Type")
  dfm2 = melt(datPlot[, c('Code', 'Device', 'cross_section_SDC_thermals_err', 'cross_section_SDC_thermals')], id.vars = c(1, 2, 3))
  colnames(dfm2) = c("Code", "Device", "Error", "Neutron_Type", "Cross_Section")
  dfm2$Neutron_Type = "Thermals (SDC)"
  dfm2$Event_Type = "SDC"
  colnames(dfm2) = c("Code", "Device", "Error", "Neutron_Type", "Cross_Section", "Event_Type")
  
  dfm3 = melt(datPlot[, c('Code', 'Device', 'cross_section_DUE_high_err', 'cross_section_DUE_high')], id.vars = c(1, 2, 3))
  colnames(dfm3) = c("Code", "Device", "Error", "Neutron_Type", "Cross_Section")
  dfm3$Neutron_Type = "High Energy (DUE)"
  dfm3$Event_Type = "DUE"
  colnames(dfm3) = c("Code", "Device", "Error", "Neutron_Type", "Cross_Section", "Event_Type")
  dfm4 = melt(datPlot[, c('Code', 'Device', 'cross_section_DUE_thermals_err', 'cross_section_DUE_thermals')], id.vars = c(1, 2, 3))
  colnames(dfm4) = c("Code", "Device", "Error", "Neutron_Type", "Cross_Section")
  dfm4$Neutron_Type = "Thermals (DUE)"
  dfm4$Event_Type = "DUE"
  colnames(dfm4) = c("Code", "Device", "Error", "Neutron_Type", "Cross_Section", "Event_Type")
  
  dfm = rbind(dfm1, dfm2, dfm3, dfm4)
  
  
  dfm$Device <- factor(dfm$Device, levels = c("K20", "TitanX", "TitanV"))
    
  dfm$Neutron_Type <- factor(dfm$Neutron_Type, levels = c("High Energy (SDC)", "Thermals (SDC)", "High Energy (DUE)", "Thermals (DUE)"))
  
  plot = ggplot(dfm, aes(x=Code, weight=Cross_Section, ymin=Cross_Section-Error, ymax=Cross_Section+Error, fill=Neutron_Type, colour=Neutron_Type)) +
  geom_bar      (position=position_dodge(), aes(y=Cross_Section), stat="identity") +
  geom_errorbar (position=position_dodge(width=0.9), width=0.2, colour="black") +
    facet_grid(~ Device, scales = "free") +
  labs(x = "", y = "Cross Section [a.u.]", fill="", color="") +
    scale_color_manual(values = c("red", "black", "red", "black")) +
    scale_fill_manual(values=c("#1f78b4", "#33a02c", "#a6cee3", "#b2df8a")) + 
    theme(legend.position="bottom")
  #theme(legend.position="bottom",axis.text.x=element_text(size=14) , axis.text.y=element_text(size=14) , text = element_text(size = 14))
  #filename = paste("./plots/FIT_SDC_", device, ".pdf", sep="")
  ggsave("./plots_final/cs_SDC_DUE_NVIDIA.pdf", plot, width = 12, height = 4)
  plot
```


### Xeon Phi

```{r}
  
  datPlot = datNormalized[datNormalized$Device == "XeonPhi", ]
  
  dfm1 = melt(datPlot[, c('Code', 'Device', 'cross_section_SDC_high_err', 'cross_section_SDC_high')], id.vars = c(1, 2, 3))
  colnames(dfm1) = c("Code", "Device", "Error", "Neutron_Type", "Cross_Section")
  dfm1$Neutron_Type = "High Energy (SDC)"
  dfm1$Event_Type = "SDC"
  colnames(dfm1) = c("Code", "Device", "Error", "Neutron_Type", "Cross_Section", "Event_Type")
  dfm2 = melt(datPlot[, c('Code', 'Device', 'cross_section_SDC_thermals_err', 'cross_section_SDC_thermals')], id.vars = c(1, 2, 3))
  colnames(dfm2) = c("Code", "Device", "Error", "Neutron_Type", "Cross_Section")
  dfm2$Neutron_Type = "Thermals (SDC)"
  dfm2$Event_Type = "SDC"
  colnames(dfm2) = c("Code", "Device", "Error", "Neutron_Type", "Cross_Section", "Event_Type")
  
  dfm3 = melt(datPlot[, c('Code', 'Device', 'cross_section_DUE_high_err', 'cross_section_DUE_high')], id.vars = c(1, 2, 3))
  colnames(dfm3) = c("Code", "Device", "Error", "Neutron_Type", "Cross_Section")
  dfm3$Neutron_Type = "High Energy (DUE)"
  dfm3$Event_Type = "DUE"
  colnames(dfm3) = c("Code", "Device", "Error", "Neutron_Type", "Cross_Section", "Event_Type")
  dfm4 = melt(datPlot[, c('Code', 'Device', 'cross_section_DUE_thermals_err', 'cross_section_DUE_thermals')], id.vars = c(1, 2, 3))
  colnames(dfm4) = c("Code", "Device", "Error", "Neutron_Type", "Cross_Section")
  dfm4$Neutron_Type = "Thermals (DUE)"
  dfm4$Event_Type = "DUE"
  colnames(dfm4) = c("Code", "Device", "Error", "Neutron_Type", "Cross_Section", "Event_Type")
  
  dfm = rbind(dfm1, dfm2, dfm3, dfm4)

  dfm$Neutron_Type <- factor(dfm$Neutron_Type, levels = c("High Energy (SDC)", "Thermals (SDC)", "High Energy (DUE)", "Thermals (DUE)"))
  
  plot = ggplot(dfm, aes(x=Code, weight=Cross_Section, ymin=Cross_Section-Error, ymax=Cross_Section+Error, fill=Neutron_Type, colour=Neutron_Type)) +
  geom_bar      (position=position_dodge(), aes(y=Cross_Section), stat="identity") +
  geom_errorbar (position=position_dodge(width=0.9), width=0.2, colour="black") +
#    facet_grid(~ Device) +
  labs(x = "", y = "Cross Section [a.u.]", fill="", color="") +
    scale_color_manual(values = c("red", "black", "red", "black")) +
    scale_fill_manual(values=c("#1f78b4", "#33a02c", "#a6cee3", "#b2df8a")) + 
    guides(color=guide_legend(nrow = 2)) +
    theme(legend.position="bottom")
  #theme(legend.position="bottom",axis.text.x=element_text(size=14) , axis.text.y=element_text(size=14) , text = element_text(size = 14))
  #filename = paste("./plots/FIT_SDC_", device, ".pdf", sep="")
  ggsave("./plots_final/cs_SDC_DUE_XeonPhi.pdf", plot, width = 5, height = 5)
  plot
```


### FPGA

```{r}
  
  datPlot = datNormalized[datNormalized$Device == "FPGA", ]
  
  dfm1 = melt(datPlot[, c('Code', 'Device', 'cross_section_SDC_high_err', 'cross_section_SDC_high')], id.vars = c(1, 2, 3))
  colnames(dfm1) = c("Code", "Device", "Error", "Neutron_Type", "Cross_Section")
  dfm1$Neutron_Type = "High Energy (SDC)"
  dfm2 = melt(datPlot[, c('Code', 'Device', 'cross_section_SDC_thermals_err', 'cross_section_SDC_thermals')], id.vars = c(1, 2, 3))
  colnames(dfm2) = c("Code", "Device", "Error", "Neutron_Type", "Cross_Section")
  dfm2$Neutron_Type = "Thermals (SDC)"
  
  dfm = rbind(dfm1, dfm2)

  dfm$Neutron_Type <- factor(dfm$Neutron_Type, levels = c("High Energy (SDC)", "Thermals (SDC)"))
  
  plot = ggplot(dfm, aes(x=Code, weight=Cross_Section, ymin=Cross_Section-Error, ymax=Cross_Section+Error, fill=Neutron_Type, colour=Neutron_Type)) +
  geom_bar      (position=position_dodge(), aes(y=Cross_Section), stat="identity") +
  geom_errorbar (position=position_dodge(width=0.9), width=0.2, colour="black") +
#    facet_grid(~ Device) +
  labs(x = "", y = "Cross Section SDC [a.u.]", fill="", color="") +
    scale_color_manual(values = c("red", "black", "red", "black")) +
    scale_fill_manual(values=c("#1f78b4", "#33a02c", "#a6cee3", "#b2df8a")) + 
    theme(legend.position="bottom")
  #theme(legend.position="bottom",axis.text.x=element_text(size=14) , axis.text.y=element_text(size=14) , text = element_text(size = 14))
  #filename = paste("./plots_final/FIT_SDC_", device, ".pdf", sep="")
  ggsave("./plots_final/cs_SDC_DUE_FPGA.pdf", plot, width = 5, height = 5)
  plot
```


#### Cross Sections Ratio ALL devices

The idea is to show the difference between the cross sections of high energy and thermals in a more "easy to compare" way. Thus, we will divide the larger one by the smaller one to show the magnitude of the difference.

First we compute the ration and save into a new column the ratio and another one which neutron type (High Energy or Thermals) is the larger one.
```{r}
datNormalized$ratioSDC = ifelse(datNormalized$cross_section_SDC_high >= datNormalized$cross_section_SDC_thermals, datNormalized$cross_section_SDC_high/datNormalized$cross_section_SDC_thermals, -datNormalized$cross_section_SDC_thermals/datNormalized$cross_section_SDC_high)
datNormalized$moreSensitiveSDC = ifelse(datNormalized$cross_section_SDC_high >= datNormalized$cross_section_SDC_thermals, "High Energy", "Thermals")

datNormalized$ratioDUE = ifelse(datNormalized$cross_section_DUE_high >= datNormalized$cross_section_DUE_thermals, datNormalized$cross_section_DUE_high/datNormalized$cross_section_DUE_thermals, -datNormalized$cross_section_DUE_thermals/datNormalized$cross_section_DUE_high)
datNormalized$moreSensitiveDUE = ifelse(datNormalized$cross_section_DUE_high >= datNormalized$cross_section_DUE_thermals, "High Energy", "Thermals")

datNormalized$ratioDUE = ifelse(datNormalized$cross_section_DUE_high == 0 | datNormalized$cross_section_DUE_thermals == 0, 0, datNormalized$ratioDUE)

for (board in unique(datNormalized$Device)) {
  
  m = mean(na.exclude(datNormalized[datNormalized$Device == board, ]$ratioSDC))
  p = 1/m
  print(paste("Device: ",board, "; m: ",m, "; p: ",p))
}


```

SDC
```{r}
  #SDC
  dfm1 = melt(datNormalized[, c('Device', 'Code', 'ratioSDC')], id.vars = c(1, 2))
  colnames(dfm1) = c("Device", "Code", "Larger", "ratio") 
  dfm1$Larger = ifelse(dfm1$ratio >= 0, "High Energy", "Thermals")
  dfm1$Event_Type = "SDC"

  
    
  dfm1[1] <- data.frame(lapply(dfm1[1], function(x) { gsub("GPUembedded", "AMD\nGPU", x) }))
  dfm1[1] <- data.frame(lapply(dfm1[1], function(x) { gsub("CPU", "AMD\nCPU", x) }))
  dfm1[1] <- data.frame(lapply(dfm1[1], function(x) { gsub("CPU+GPU", "AMD\nCPU+GPU", x) }))
  dfm1[1] <- data.frame(lapply(dfm1[1], function(x) { gsub("XeonPhi", "Xeon Phi", x) }))

  # changing factor order
  dfm1$Device <- factor(dfm1$Device, levels = c("AMD\nCPU", "AMD\nGPU", "AMD\nCPU+GPU", "K20", "TitanX", "TitanV", "Xeon Phi", "FPGA"))
  
  #DUE
  dfm2 = melt(datNormalized[, c('Device', 'Code', 'ratioDUE')], id.vars = c(1, 2))
  dfm2 = dfm2[complete.cases(dfm2), ]
  
  colnames(dfm2) = c("Device", "Code", "Larger", "ratio") 
  dfm2$Larger = ifelse(dfm2$ratio >= 0, "High Energy", "Thermals")
  dfm2$Event_Type = "DUE"
  dfm2 = dfm2[dfm2$ratio!=0, ] # removing lavamd from titanV which is 0 but actually should be NA

  
    
  dfm2[1] <- data.frame(lapply(dfm2[1], function(x) { gsub("GPUembedded", "AMD\nGPU", x) }))
  dfm2[1] <- data.frame(lapply(dfm2[1], function(x) { gsub("CPU", "AMD\nCPU", x) }))
  dfm2[1] <- data.frame(lapply(dfm2[1], function(x) { gsub("CPU+GPU", "AMD\nCPU+GPU", x) }))
  dfm2[1] <- data.frame(lapply(dfm2[1], function(x) { gsub("XeonPhi", "Xeon Phi", x) }))

  # changing factor order
  dfm2$Device <- factor(dfm2$Device, levels = c("AMD\nCPU", "AMD\nGPU", "AMD\nCPU+GPU", "K20", "TitanX", "TitanV", "Xeon Phi", "FPGA"))

  dfm = rbind(dfm1, dfm2)
  
plot = ggplot(dfm, aes(x=Code, y=ratio, fill=Larger)) +
  geom_bar(stat="identity") +
  facet_grid(Device ~ Event_Type, scales = "free") +
  coord_flip() +
  labs(x = "Code", y = "Cross Section SDC Ratio", fill="") +
  theme(legend.position="bottom")
  ggsave("./plots_final/ratio-SDC-DUE_all.pdf",plot, width = 12, height = 7)
plot
```


DUE
```{r}
  dfm1 = melt(datNormalized[, c('Device', 'Code', 'ratioDUE')], id.vars = c(1, 2))
  dfm1 = dfm1[complete.cases(dfm1), ]
  
  colnames(dfm1) = c("Device", "Code", "Larger", "ratioDUE") 
  dfm1$Larger = ifelse(dfm1$ratioDUE >= 0, "High Energy", "Thermals")
  dfm1 = dfm1[dfm1$ratioDUE!=0, ] # removing lavamd from titanV which is 0 but actually should be NA

  
    
  dfm1[1] <- data.frame(lapply(dfm1[1], function(x) { gsub("GPUembedded", "AMD\nGPU", x) }))
  dfm1[1] <- data.frame(lapply(dfm1[1], function(x) { gsub("CPU", "AMD\nCPU", x) }))
  dfm1[1] <- data.frame(lapply(dfm1[1], function(x) { gsub("CPU+GPU", "AMD\nCPU+GPU", x) }))
  dfm1[1] <- data.frame(lapply(dfm1[1], function(x) { gsub("XeonPhi", "Xeon Phi", x) }))

  # changing factor order
  dfm1$Device <- factor(dfm1$Device, levels = c("AMD\nCPU", "AMD\nGPU", "AMD\nCPU+GPU", "K20", "TitanX", "TitanV", "Xeon Phi", "FPGA"))
  

plot = ggplot(dfm1, aes(x=Code, y=ratioDUE, fill=Larger)) +
  geom_bar(stat="identity") +
  facet_grid(Device ~ ., scales = "free") +
  coord_flip() +
  labs(x = "Code", y = "Cross Section DUE Ratio", fill="") +
  theme(legend.position="bottom")
#ggsave("./plots_final/ratio-DUE-thermals-vs-high-all.pdf",plot)
plot
```


