---
title: "DSN 2019"
author: "Daniel"
date: "November 17, 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading data and libraries

Load ggplot2 for plotting data and the CSV file with all data. We also correct the cross section of thermals since the rotax spectrum is different, which means we should correct the fluence we had before by a factor of (4.96/2.71). Thus, we divide the cross section by this factor since the cross section is (number of errors)/(fluence).

```{r}
library(ggplot2)

dat = read.csv("data_formatted.csv",sep=",")

dat$cross_section_SDC_thermals = dat$cross_section_SDC_thermals / (4.96/2.71)

summary(dat)
```


## Normalize SDC and DUE Cross Sections

Find the minimum value for each device and normalize SDC and DUE cross sections. Then, append the values normalize to a new data frame called "datNormalized"

```{r}
datNormalized = dat
for (board in unique(dat$Device)) {
  # Get all cross section values for one device
  tmp_values = c(subset(dat,dat$Device==board)$cross_section_SDC_high, subset(dat,dat$Device==board)$cross_section_DUE_high, subset(dat,dat$Device==board)$cross_section_SDC_thermals, subset(dat,dat$Device==board)$cross_section_DUE_thermals)
  tmp_values = tmp_values[tmp_values > 0] # remove zeros in case there is zeros
  tmp_min = min(tmp_values, na.rm=TRUE) # get the minimum cross section value
  print(paste("Device: ", board, "; Minimum: ",tmp_min))
  
  # Normalize all date from one device to the minimum value found
  datNormalized[datNormalized$Device == board, ]$cross_section_SDC_high = datNormalized[datNormalized$Device == board, ]$cross_section_SDC_high / tmp_min
  datNormalized[datNormalized$Device == board, ]$cross_section_DUE_high = datNormalized[datNormalized$Device == board, ]$cross_section_DUE_high / tmp_min
  datNormalized[datNormalized$Device == board, ]$cross_section_SDC_thermals = datNormalized[datNormalized$Device == board, ]$cross_section_SDC_thermals / tmp_min
  datNormalized[datNormalized$Device == board, ]$cross_section_DUE_thermals = datNormalized[datNormalized$Device == board, ]$cross_section_DUE_thermals / tmp_min
}
```




## Compute FIT for High Energy

Normal flux is 13 neutrons per cm^2 per hour. Since data is normalized, there is no need to multiply by 10^9

```{r}
datNormalized$FIT_SDC_high = datNormalized$cross_section_SDC_high * 13
datNormalized$FIT_DUE_high = datNormalized$cross_section_DUE_high * 13
```

## Compute FIT for Thermals


Normal flux is 4 neutrons per cm^2 per hour under normal environments. 

```{r}
datNormalized$FIT_SDC_thermals = datNormalized$cross_section_SDC_thermals * 4
datNormalized$FIT_DUE_thermals = datNormalized$cross_section_DUE_thermals * 4
```

During a thunderstrom the neutron flux is about 8 neutrons

```{r}
datNormalized$FIT_SDC_thermals_storm = datNormalized$cross_section_SDC_thermals * 8
datNormalized$FIT_DUE_thermals_storm = datNormalized$cross_section_DUE_thermals * 8
```

## Compute the error bars

Using the Poisson distribution with 95% confidence, which is  1.96*sqrt(test_mean/#tests)

```{r}
  datNormalized$cross_section_SDC_high_err = 1.96*sqrt(datNormalized$cross_section_SDC_high/datNormalized$number_SDCs_high)
  datNormalized$cross_section_DUE_high_err = 1.96*sqrt(datNormalized$cross_section_DUE_high/datNormalized$number_DUE_high)

  datNormalized$cross_section_SDC_thermals_err = 1.96*sqrt(datNormalized$cross_section_SDC_thermals/datNormalized$number_SDCs_thermals)
  datNormalized$cross_section_DUE_thermals_err = 1.96*sqrt(datNormalized$cross_section_DUE_thermals/datNormalized$number_DUE_thermals)
  
  datNormalized$FIT_SDC_high_err = 1.96*sqrt(datNormalized$FIT_SDC_high/datNormalized$number_SDCs_high)
  datNormalized$FIT_DUE_high_err = 1.96*sqrt(datNormalized$FIT_DUE_high/datNormalized$number_DUE_high)

  datNormalized$FIT_DUE_thermals_err = 1.96*sqrt(datNormalized$FIT_DUE_thermals/datNormalized$number_DUE_thermals)
  datNormalized$FIT_SDC_thermals_err = 1.96*sqrt(datNormalized$FIT_SDC_thermals/datNormalized$number_SDCs_thermals)

  datNormalized$FIT_SDC_thermals_storm_err = 1.96*sqrt(datNormalized$FIT_SDC_thermals_storm/datNormalized$number_SDCs_thermals)
  datNormalized$FIT_DUE_thermals_storm_err = 1.96*sqrt(datNormalized$FIT_DUE_thermals_storm/datNormalized$number_DUE_thermals)
```


## Plots

### Cross Sections

#### Function to plot Cross Sections

Melt the data frame to plot two columns for each code and plot them with error bars

```{r}
library(reshape2)

cs_sdc_plot_errbars <- function(device){
  datPlot = datNormalized[datNormalized$Device == device, ]
  
  dfm1 = melt(datPlot[, c('Code', 'cross_section_SDC_high_err', 'cross_section_SDC_high')], id.vars = c(1, 2))
  colnames(dfm1) = c("Code", "Error", "Neutron_Type", "Cross_Section")
  dfm1$Neutron_Type = "High Energy"
  dfm2 = melt(datPlot[, c('Code', 'cross_section_SDC_thermals_err', 'cross_section_SDC_thermals')], id.vars = c(1, 2))
  colnames(dfm2) = c("Code", "Error", "Neutron_Type", "Cross_Section")
  dfm2$Neutron_Type = "Thermals"
  dfm = rbind(dfm1, dfm2)
  
  plot = ggplot(dfm, aes(x=Code, weight=Cross_Section, ymin=Cross_Section-Error, ymax=Cross_Section+Error, fill=Neutron_Type)) +
  geom_bar      (position=position_dodge(), aes(y=Cross_Section), stat="identity") +
  geom_errorbar (position=position_dodge(width=0.9), width=0.2, colour="black") +
  labs(x = "", y = "Cross Section SDC [a.u.]", fill="") +
  theme(legend.position="bottom",axis.text.x=element_text(size=14) , axis.text.y=element_text(size=14) , text = element_text(size = 14))
  filename = paste("./plots/cs_SDC_", device, ".pdf", sep="")
  ggsave(filename, plot)
  plot
}

cs_due_plot_errbars <- function(device){
  datPlot = datNormalized[datNormalized$Device == device, ]
  
  dfm1 = melt(datPlot[, c('Code', 'cross_section_DUE_high_err', 'cross_section_DUE_high')], id.vars = c(1, 2))
  colnames(dfm1) = c("Code", "Error", "Neutron_Type", "Cross_Section")
  dfm1$Neutron_Type = "High Energy"
  dfm2 = melt(datPlot[, c('Code', 'cross_section_DUE_thermals_err', 'cross_section_DUE_thermals')], id.vars = c(1, 2))
  colnames(dfm2) = c("Code", "Error", "Neutron_Type", "Cross_Section")
  dfm2$Neutron_Type = "Thermals"
  dfm = rbind(dfm1, dfm2)
  
  plot = ggplot(dfm, aes(x=Code, weight=Cross_Section, ymin=Cross_Section-Error, ymax=Cross_Section+Error, fill=Neutron_Type)) +
    geom_bar      (position=position_dodge(), aes(y=Cross_Section), stat="identity") +
    geom_errorbar (position=position_dodge(width=0.9), width=0.2, colour="black") +
    #labs(title = plot_title, x = "", y = "Cross Section DUE [a.u.]", fill="") +
    labs(x = "", y = "Cross Section DUE [a.u.]", fill="") +
    theme(legend.position="bottom",axis.text.x=element_text(size=14) , axis.text.y=element_text(size=14) , text = element_text(size = 14))
  #theme(plot.title = element_text(hjust = 0.5), legend.position="bottom",axis.text.x=element_text(size=14) , axis.text.y=element_text(size=14) , text = element_text(size = 14))
  filename = paste("./plots/cs_DUE_", device, ".pdf", sep="")
  ggsave(filename, plot)
  plot
}

```

#### Plot Cross Sections

##### APUs
SDC
```{r}
  datPlot = subset(datNormalized, Device=="CPU" | Device == "GPUembedded" | Device == "CPU+GPU")
  
  dfm1 = melt(datPlot[, c('Code', 'Device', 'cross_section_SDC_high_err', 'cross_section_SDC_high')], id.vars = c(1, 2, 3))
  colnames(dfm1) = c("Code", "Device", "Error", "Neutron_Type", "Cross_Section")
  dfm1$Neutron_Type = "High Energy"
  dfm2 = melt(datPlot[, c('Code', 'Device', 'cross_section_SDC_thermals_err', 'cross_section_SDC_thermals')], id.vars = c(1, 2, 3))
  colnames(dfm2) = c("Code", "Device", "Error", "Neutron_Type", "Cross_Section")
  dfm2$Neutron_Type = "Thermals"
  dfm = rbind(dfm1, dfm2)
  
  dfm[2] <- data.frame(lapply(dfm[2], function(x) { gsub("GPUembedded", "AMD\nGPU", x) }))
  dfm[2] <- data.frame(lapply(dfm[2], function(x) { gsub("CPU", "AMD\nCPU", x) }))
  dfm[2] <- data.frame(lapply(dfm[2], function(x) { gsub("CPU+GPU", "AMD\nCPU+GPU", x) }))
  
  dfm$Device <- factor(dfm$Device, levels = c("AMD\nCPU", "AMD\nGPU", "AMD\nCPU+GPU"))
  
  plot = ggplot(dfm, aes(x=Code, weight=Cross_Section, ymin=Cross_Section-Error, ymax=Cross_Section+Error, fill=Neutron_Type)) +
  geom_bar      (position=position_dodge(), aes(y=Cross_Section), stat="identity") +
  geom_errorbar (position=position_dodge(width=0.9), width=0.2, colour="black") +
    facet_grid(~ Device) +
  labs(x = "", y = "Cross Section SDC [a.u.]", fill="") +
    theme(legend.position="bottom")
  #theme(legend.position="bottom",axis.text.x=element_text(size=14) , axis.text.y=element_text(size=14) , text = element_text(size = 14))
  #filename = paste("./plots/FIT_SDC_", device, ".pdf", sep="")
  ggsave("./plots/cs_SDC_APU.pdf", plot, width = 12, height = 7)
  plot
```

DUE
```{r}
  datPlot = subset(datNormalized, Device=="CPU" | Device == "GPUembedded" | Device == "CPU+GPU")
  
  dfm1 = melt(datPlot[, c('Code', 'Device', 'cross_section_DUE_high_err', 'cross_section_DUE_high')], id.vars = c(1, 2, 3))
  colnames(dfm1) = c("Code", "Device", "Error", "Neutron_Type", "Cross_Section")
  dfm1$Neutron_Type = "High Energy"
  dfm2 = melt(datPlot[, c('Code', 'Device', 'cross_section_DUE_thermals_err', 'cross_section_DUE_thermals')], id.vars = c(1, 2, 3))
  colnames(dfm2) = c("Code", "Device", "Error", "Neutron_Type", "Cross_Section")
  dfm2$Neutron_Type = "Thermals"
  dfm = rbind(dfm1, dfm2)
  
  dfm[2] <- data.frame(lapply(dfm[2], function(x) { gsub("GPUembedded", "AMD\nGPU", x) }))
  dfm[2] <- data.frame(lapply(dfm[2], function(x) { gsub("CPU", "AMD\nCPU", x) }))
  dfm[2] <- data.frame(lapply(dfm[2], function(x) { gsub("CPU+GPU", "AMD\nCPU+GPU", x) }))
  
  dfm$Device <- factor(dfm$Device, levels = c("AMD\nCPU", "AMD\nGPU", "AMD\nCPU+GPU"))
  
  plot = ggplot(dfm, aes(x=Code, weight=Cross_Section, ymin=Cross_Section-Error, ymax=Cross_Section+Error, fill=Neutron_Type)) +
  geom_bar      (position=position_dodge(), aes(y=Cross_Section), stat="identity") +
  geom_errorbar (position=position_dodge(width=0.9), width=0.2, colour="black") +
    facet_grid(~ Device) +
  labs(x = "", y = "Cross Section DUE [a.u.]", fill="") +
    theme(legend.position="bottom")
  #theme(legend.position="bottom",axis.text.x=element_text(size=14) , axis.text.y=element_text(size=14) , text = element_text(size = 14))
  #filename = paste("./plots/FIT_SDC_", device, ".pdf", sep="")
  ggsave("./plots/cs_DUE_APU.pdf", plot, width = 12, height = 7)
  plot
```

##### NVIDIA
SDC
```{r}
   datPlot = subset(datNormalized, Device=="K20" | Device == "TitanV" | Device == "TitanX")

  dfm1 = melt(datPlot[, c('Code', 'Device', 'cross_section_SDC_high_err', 'cross_section_SDC_high')], id.vars = c(1, 2, 3))
  colnames(dfm1) = c("Code", "Device", "Error", "Neutron_Type", "Cross_Section")
  dfm1$Neutron_Type = "High Energy"
  dfm2 = melt(datPlot[, c('Code', 'Device', 'cross_section_SDC_thermals_err', 'cross_section_SDC_thermals')], id.vars = c(1, 2, 3))
  colnames(dfm2) = c("Code", "Device", "Error", "Neutron_Type", "Cross_Section")
  dfm2$Neutron_Type = "Thermals"
  dfm = rbind(dfm1, dfm2)
  
  dfm$Device <- factor(dfm$Device, levels = c("K20", "TitanX", "TitanV"))
  
  plot = ggplot(dfm, aes(x=Code, weight=Cross_Section, ymin=Cross_Section-Error, ymax=Cross_Section+Error, fill=Neutron_Type)) +
  geom_bar      (position=position_dodge(), aes(y=Cross_Section), stat="identity") +
  geom_errorbar (position=position_dodge(width=0.9), width=0.2, colour="black") +
    facet_grid(~ Device) +
  labs(x = "", y = "Cross Section SDC [a.u.]", fill="") +
    theme(legend.position="bottom")
  #theme(legend.position="bottom",axis.text.x=element_text(size=14) , axis.text.y=element_text(size=14) , text = element_text(size = 14))
  #filename = paste("./plots/FIT_SDC_", device, ".pdf", sep="")
  ggsave("./plots/cs_SDC_NVIDIA.pdf", plot, width = 12, height = 7)
  plot
```
DUE
```{r}
   datPlot = subset(datNormalized, Device=="K20" | Device == "TitanV" | Device == "TitanX")

  dfm1 = melt(datPlot[, c('Code', 'Device', 'cross_section_DUE_high_err', 'cross_section_DUE_high')], id.vars = c(1, 2, 3))
  colnames(dfm1) = c("Code", "Device", "Error", "Neutron_Type", "Cross_Section")
  dfm1$Neutron_Type = "High Energy"
  dfm2 = melt(datPlot[, c('Code', 'Device', 'cross_section_DUE_thermals_err', 'cross_section_DUE_thermals')], id.vars = c(1, 2, 3))
  colnames(dfm2) = c("Code", "Device", "Error", "Neutron_Type", "Cross_Section")
  dfm2$Neutron_Type = "Thermals"
  dfm = rbind(dfm1, dfm2)
  
  dfm$Device <- factor(dfm$Device, levels = c("K20", "TitanX", "TitanV"))
  
  plot = ggplot(dfm, aes(x=Code, weight=Cross_Section, ymin=Cross_Section-Error, ymax=Cross_Section+Error, fill=Neutron_Type)) +
  geom_bar      (position=position_dodge(), aes(y=Cross_Section), stat="identity") +
  geom_errorbar (position=position_dodge(width=0.9), width=0.2, colour="black") +
    facet_grid(~ Device) +
  labs(x = "", y = "Cross Section DUE [a.u.]", fill="") +
    theme(legend.position="bottom")
  #theme(legend.position="bottom",axis.text.x=element_text(size=14) , axis.text.y=element_text(size=14) , text = element_text(size = 14))
  #filename = paste("./plots/FIT_SDC_", device, ".pdf", sep="")
  ggsave("./plots/cs_DUE_NVIDIA.pdf", plot, width = 12, height = 7)
  plot
```

##### Titan X 
SDC
```{r}
cs_sdc_plot_errbars("TitanX")
```

DUE
```{r}
cs_due_plot_errbars("TitanX")
```

##### Titan V 
SDC
```{r}
cs_sdc_plot_errbars("TitanV")
```

DUE
```{r}
cs_due_plot_errbars("TitanV")
```

##### K20 
SDC
```{r}
cs_sdc_plot_errbars("K20")
```

DUE
```{r}
cs_due_plot_errbars("K20")
```

##### Xeon Phi 
SDC
```{r}
cs_sdc_plot_errbars("XeonPhi")
```

DUE
```{r}
cs_due_plot_errbars("XeonPhi")
```

##### CPU 
SDC
```{r}
cs_sdc_plot_errbars("CPU")
```

DUE
```{r}
cs_due_plot_errbars("CPU")
```

##### GPU 
SDC
```{r}
cs_sdc_plot_errbars("GPUembedded")
```

DUE
```{r}
cs_due_plot_errbars("GPUembedded")
```

##### CPU+GPU 

SDC
```{r}
cs_sdc_plot_errbars("CPU+GPU")
```

DUE
```{r}
cs_due_plot_errbars("CPU+GPU")
```

##### FPGA

SDC
```{r}
cs_sdc_plot_errbars("FPGA")
```

There is no DUE for FPGAs

### Cross Section Ratio

The idea is to show the difference between the cross sections of high energy and thermals in a more "easy to compare" way. Thus, we will divide the larger one by the smaller one to show the magnitude of the difference.

First we compute the ration and save into a new column the ratio and another one which neutron type (High Energy or Thermals) is the larger one.
```{r}
datNormalized$ratioSDC = ifelse(datNormalized$cross_section_SDC_high >= datNormalized$cross_section_SDC_thermals, datNormalized$cross_section_SDC_high/datNormalized$cross_section_SDC_thermals, -datNormalized$cross_section_SDC_thermals/datNormalized$cross_section_SDC_high)
datNormalized$moreSensitiveSDC = ifelse(datNormalized$cross_section_SDC_high >= datNormalized$cross_section_SDC_thermals, "High Energy", "Thermals")

datNormalized$ratioDUE = ifelse(datNormalized$cross_section_DUE_high >= datNormalized$cross_section_DUE_thermals, datNormalized$cross_section_DUE_high/datNormalized$cross_section_DUE_thermals, -datNormalized$cross_section_DUE_thermals/datNormalized$cross_section_DUE_high)
datNormalized$moreSensitiveDUE = ifelse(datNormalized$cross_section_DUE_high >= datNormalized$cross_section_DUE_thermals, "High Energy", "Thermals")

datNormalized$ratioDUE = ifelse(datNormalized$cross_section_DUE_high == 0 | datNormalized$cross_section_DUE_thermals == 0, 0, datNormalized$ratioDUE)

```

Now the functions to plot the data

```{r}
cs_sdc_ratio <- function(device){
  plot = ggplot(datNormalized[datNormalized$Device == device, ], aes(x=Code, y=ratioSDC, fill=moreSensitiveSDC)) +
    geom_bar(stat="identity") +
    labs(x = "", y = "Cross Section SDC Ratio", fill="") + 
    theme(legend.position="bottom",axis.text.x=element_text(size=14) , axis.text.y=element_text(size=14) , text = element_text(size = 14))
  
  filename = paste("./plots/cs_ratio_SDC_", device, ".pdf", sep="")
  ggsave(filename, plot)
  plot
}

cs_due_ratio <- function(device){
  plot = ggplot(datNormalized[datNormalized$Device == device, ], aes(x=Code, y=ratioDUE, fill=moreSensitiveDUE)) +
    geom_bar(stat="identity") +
    labs(x = "", y = "Cross Section DUE Ratio", fill="") +
    theme(legend.position="bottom",axis.text.x=element_text(size=14) , axis.text.y=element_text(size=14) , text = element_text(size = 14))
  
  filename = paste("./plots/cs_ratio_DUE_", device, ".pdf", sep="")
  ggsave(filename, plot)
  plot
}
```

<!-- We don't need a ratio plot for each device
#### Xeon Phi

SDC 
```{r}
cs_sdc_ratio("XeonPhi")
```

DUE 
```{r}
cs_due_ratio("XeonPhi")
```

#### TitanV
SDC
```{r}
cs_sdc_ratio("TitanV")
```

DUE
```{r}
cs_due_ratio("TitanV")
```

#### TitanX
SDC
```{r}
cs_sdc_ratio("TitanX")
```

DUE
```{r}
cs_due_ratio("TitanX")
```

#### K20
SDC
```{r}
cs_sdc_ratio("K20")
```

DUE
```{r}
cs_due_ratio("K20")
```

#### CPU
SDC
```{r}
cs_sdc_ratio("CPU")
```

DUE
```{r}
cs_due_ratio("CPU")
```

#### GPUembedded
SDC
```{r}
cs_sdc_ratio("GPUembedded")
```

DUE
```{r}
cs_due_ratio("GPUembedded")
```

#### CPU+GPU
SDC
```{r}
cs_sdc_ratio("CPU+GPU")
```

DUE
```{r}
cs_due_ratio("CPU+GPU")
```

#### FPGA
SDC
```{r}
cs_sdc_ratio("FPGA")
```


-->

#### Cross Sections Ratio ALL devices

SDC
```{r}
  dfm1 = melt(datNormalized[, c('Device', 'Code', 'ratioSDC')], id.vars = c(1, 2))
  colnames(dfm1) = c("Device", "Code", "Larger", "ratioSDC") 
  dfm1$Larger = ifelse(dfm1$ratioSDC >= 0, "High Energy", "Thermals")

  
    
  dfm1[1] <- data.frame(lapply(dfm1[1], function(x) { gsub("GPUembedded", "AMD\nGPU", x) }))
  dfm1[1] <- data.frame(lapply(dfm1[1], function(x) { gsub("CPU", "AMD\nCPU", x) }))
  dfm1[1] <- data.frame(lapply(dfm1[1], function(x) { gsub("CPU+GPU", "AMD\nCPU+GPU", x) }))
  dfm1[1] <- data.frame(lapply(dfm1[1], function(x) { gsub("XeonPhi", "Xeon Phi", x) }))

  # changing factor order
  dfm1$Device <- factor(dfm1$Device, levels = c("AMD\nCPU", "AMD\nGPU", "AMD\nCPU+GPU", "K20", "TitanX", "TitanV", "Xeon Phi", "FPGA"))
  

plot = ggplot(dfm1, aes(x=Code, y=ratioSDC, fill=Larger)) +
  geom_bar(stat="identity") +
  facet_grid(Device ~ ., scales = "free") +
  coord_flip() +
  labs(x = "Code", y = "Cross Section SDC Ratio", fill="") +
  theme(legend.position="bottom")
ggsave("./plots/ratio-SDC-thermals-vs-high-all.pdf",plot)
plot
```


DUE
```{r}
  dfm1 = melt(datNormalized[, c('Device', 'Code', 'ratioDUE')], id.vars = c(1, 2))
  dfm1 = dfm1[complete.cases(dfm1), ]
  
  colnames(dfm1) = c("Device", "Code", "Larger", "ratioDUE") 
  dfm1$Larger = ifelse(dfm1$ratioDUE >= 0, "High Energy", "Thermals")
  dfm1 = dfm1[dfm1$ratioDUE!=0, ] # removing lavamd from titanV which is 0 but actually should be NA

  
    
  dfm1[1] <- data.frame(lapply(dfm1[1], function(x) { gsub("GPUembedded", "AMD\nGPU", x) }))
  dfm1[1] <- data.frame(lapply(dfm1[1], function(x) { gsub("CPU", "AMD\nCPU", x) }))
  dfm1[1] <- data.frame(lapply(dfm1[1], function(x) { gsub("CPU+GPU", "AMD\nCPU+GPU", x) }))
  dfm1[1] <- data.frame(lapply(dfm1[1], function(x) { gsub("XeonPhi", "Xeon Phi", x) }))

  # changing factor order
  dfm1$Device <- factor(dfm1$Device, levels = c("AMD\nCPU", "AMD\nGPU", "AMD\nCPU+GPU", "K20", "TitanX", "TitanV", "Xeon Phi", "FPGA"))
  

plot = ggplot(dfm1, aes(x=Code, y=ratioDUE, fill=Larger)) +
  geom_bar(stat="identity") +
  facet_grid(Device ~ ., scales = "free") +
  coord_flip() +
  labs(x = "Code", y = "Cross Section DUE Ratio", fill="") +
  theme(legend.position="bottom")
ggsave("./plots/ratio-DUE-thermals-vs-high-all.pdf",plot)
plot
```

### FIT

#### Functions to plot FIT data

```{r}

fit_sdc_plot_errbars <- function(device){
  datPlot = datNormalized[datNormalized$Device == device, ]
  
  dfm1 = melt(datPlot[, c('Code', 'FIT_SDC_high_err', 'FIT_SDC_high')], id.vars = c(1, 2))
  colnames(dfm1) = c("Code", "Error", "Neutron_Type", "FIT")
  dfm1$Neutron_Type = "High Energy"
  dfm2 = melt(datPlot[, c('Code', 'FIT_SDC_thermals_err', 'FIT_SDC_thermals')], id.vars = c(1, 2))
  colnames(dfm2) = c("Code", "Error", "Neutron_Type", "FIT")
  dfm2$Neutron_Type = "Thermals"
  dfm3 = melt(datPlot[, c('Code', 'FIT_SDC_thermals_storm_err', 'FIT_SDC_thermals_storm')], id.vars = c(1, 2))
  colnames(dfm3) = c("Code", "Error", "Neutron_Type", "FIT")
  dfm3$Neutron_Type = "Thermals (Storm)"
  dfm = rbind(dfm1, dfm2, dfm3)
  
  plot = ggplot(dfm, aes(x=Code, weight=FIT, ymin=FIT-Error, ymax=FIT+Error, fill=Neutron_Type)) +
  geom_bar      (position=position_dodge(), aes(y=FIT), stat="identity") +
  geom_errorbar (position=position_dodge(width=0.9), width=0.2, colour="black") +
  labs(x = "", y = "FIT SDC [a.u.]", fill="") +
  theme(legend.position="bottom",axis.text.x=element_text(size=14) , axis.text.y=element_text(size=14) , text = element_text(size = 14))
  filename = paste("./plots/FIT_SDC_", device, ".pdf", sep="")
  ggsave(filename, plot)
  plot
}

fit_due_plot_errbars <- function(device){
  datPlot = datNormalized[datNormalized$Device == device, ]
  
  dfm1 = melt(datPlot[, c('Code', 'FIT_DUE_high_err', 'FIT_DUE_high')], id.vars = c(1, 2))
  colnames(dfm1) = c("Code", "Error", "Neutron_Type", "FIT")
  dfm1$Neutron_Type = "High Energy"
  dfm2 = melt(datPlot[, c('Code', 'FIT_DUE_thermals_err', 'FIT_DUE_thermals')], id.vars = c(1, 2))
  colnames(dfm2) = c("Code", "Error", "Neutron_Type", "FIT")
  dfm2$Neutron_Type = "Thermals"
  dfm3 = melt(datPlot[, c('Code', 'FIT_DUE_thermals_storm_err', 'FIT_DUE_thermals_storm')], id.vars = c(1, 2))
  colnames(dfm3) = c("Code", "Error", "Neutron_Type", "FIT")
  dfm3$Neutron_Type = "Thermals (Storm)"
  dfm = rbind(dfm1, dfm2, dfm3)
  
  plot = ggplot(dfm, aes(x=Code, weight=FIT, ymin=FIT-Error, ymax=FIT+Error, fill=Neutron_Type)) +
  geom_bar      (position=position_dodge(), aes(y=FIT), stat="identity") +
  geom_errorbar (position=position_dodge(width=0.9), width=0.2, colour="black") +
  labs(x = "", y = "FIT DUE [a.u.]", fill="") +
  theme(legend.position="bottom",axis.text.x=element_text(size=14) , axis.text.y=element_text(size=14) , text = element_text(size = 14))
  filename = paste("./plots/FIT_DUE_", device, ".pdf", sep="")
  ggsave(filename, plot)
  plot
}

sdcplot <- function(device){
datPlot = datNorm[datNorm$Device == device, ]
  plot = ggplot(datPlot, aes(x=datPlot$Code, y=datPlot$FITSDC, fill=Neutron_type)) +
  geom_bar(stat="identity", position="dodge") + 
  labs(title = device, x = "", y = "FIT SDC [a.u.]", fill="") + 
  theme(plot.title = element_text(hjust = 0.5), legend.position="bottom",axis.text.x=element_text(size=14) , axis.text.y=element_text(size=14) , text = element_text(size = 14))  
  filename = paste("~/plots/FIT-SDC-", device, ".pdf", sep="")
  ggsave(filename, plot)
  plot
}

dueplot <- function(device){
  datPlot = datNorm[datNorm$Device == device, ]
  plot = ggplot(datPlot, aes(x=datPlot$Code, y=datPlot$FITCrash, fill=Neutron_type)) +
  geom_bar(stat="identity", position="dodge") + 
  labs(title = device, x = "", y = "FIT DUE [a.u.]", fill="") + 
  theme(plot.title = element_text(hjust = 0.5), legend.position="bottom",axis.text.x=element_text(size=14) , axis.text.y=element_text(size=14) , text = element_text(size = 14))
  filename = paste("~/plots/FIT-DUE-", device, ".pdf", sep="")
  ggsave(filename, plot)
  plot
}
```

#### Plots

##### APU
SDC
```{r}
   datPlot = subset(datNormalized, Device=="CPU" | Device == "GPUembedded" | Device == "CPU+GPU")

  dfm1 = melt(datPlot[, c('Code', 'Device', 'FIT_SDC_high_err', 'FIT_SDC_high')], id.vars = c(1, 2, 3))
  colnames(dfm1) = c("Code", "Device", "Error", "Neutron_Type", "FIT")
  dfm1$Neutron_Type = "High Energy"
  dfm2 = melt(datPlot[, c('Code', 'Device', 'FIT_SDC_thermals_err', 'FIT_SDC_thermals')], id.vars = c(1, 2, 3))
  colnames(dfm2) = c("Code", "Device", "Error", "Neutron_Type", "FIT")
  dfm2$Neutron_Type = "Thermals"
  dfm3 = melt(datPlot[, c('Code', 'Device', 'FIT_SDC_thermals_storm_err', 'FIT_SDC_thermals_storm')], id.vars = c(1, 2, 3))
  colnames(dfm3) = c("Code", "Device", "Error", "Neutron_Type", "FIT")
  dfm3$Neutron_Type = "Thermals (Storm)"
  dfm = rbind(dfm1, dfm2, dfm3)
  
  dfm[2] <- data.frame(lapply(dfm[2], function(x) { gsub("GPUembedded", "AMD\nGPU", x) }))
  dfm[2] <- data.frame(lapply(dfm[2], function(x) { gsub("CPU", "AMD\nCPU", x) }))
  dfm[2] <- data.frame(lapply(dfm[2], function(x) { gsub("CPU+GPU", "AMD\nCPU+GPU", x) }))
  

  # changing factor order
  dfm$Device <- factor(dfm$Device, levels = c("AMD\nCPU", "AMD\nGPU", "AMD\nCPU+GPU"))
  
  
  plot = ggplot(dfm, aes(x=Code, weight=FIT, ymin=FIT-Error, ymax=FIT+Error, fill=Neutron_Type)) +
  geom_bar      (position=position_dodge(), aes(y=FIT), stat="identity") +
  geom_errorbar (position=position_dodge(width=0.9), width=0.2, colour="black") +
    facet_grid(~ Device) +
  labs(x = "", y = "FIT SDC [a.u.]", fill="") + 
    theme(legend.position="bottom")
  #theme(legend.position="bottom",axis.text.x=element_text(size=14) , axis.text.y=element_text(size=14) , text = element_text(size = 14))
  #filename = paste("./plots/FIT_SDC_", device, ".pdf", sep="")
  ggsave("./plots/FIT_SDC_APU.pdf", plot, width = 12, height = 7)
  plot
  

```

DUE
```{r}
   datPlot = subset(datNormalized, Device=="CPU" | Device == "GPUembedded" | Device == "CPU+GPU")

  dfm1 = melt(datPlot[, c('Code', 'Device', 'FIT_DUE_high_err', 'FIT_DUE_high')], id.vars = c(1, 2, 3))
  colnames(dfm1) = c("Code", "Device", "Error", "Neutron_Type", "FIT")
  dfm1$Neutron_Type = "High Energy"
  dfm2 = melt(datPlot[, c('Code', 'Device', 'FIT_DUE_thermals_err', 'FIT_DUE_thermals')], id.vars = c(1, 2, 3))
  colnames(dfm2) = c("Code", "Device", "Error", "Neutron_Type", "FIT")
  dfm2$Neutron_Type = "Thermals"
  dfm3 = melt(datPlot[, c('Code', 'Device', 'FIT_DUE_thermals_storm_err', 'FIT_DUE_thermals_storm')], id.vars = c(1, 2, 3))
  colnames(dfm3) = c("Code", "Device", "Error", "Neutron_Type", "FIT")
  dfm3$Neutron_Type = "Thermals (Storm)"
  dfm = rbind(dfm1, dfm2, dfm3)
  
  dfm[2] <- data.frame(lapply(dfm[2], function(x) { gsub("GPUembedded", "AMD\nGPU", x) }))
  dfm[2] <- data.frame(lapply(dfm[2], function(x) { gsub("CPU", "AMD\nCPU", x) }))
  dfm[2] <- data.frame(lapply(dfm[2], function(x) { gsub("CPU+GPU", "AMD\nCPU+GPU", x) }))
  

  # changing factor order
  dfm$Device <- factor(dfm$Device, levels = c("AMD\nCPU", "AMD\nGPU", "AMD\nCPU+GPU"))
  
  
  plot = ggplot(dfm, aes(x=Code, weight=FIT, ymin=FIT-Error, ymax=FIT+Error, fill=Neutron_Type)) +
  geom_bar      (position=position_dodge(), aes(y=FIT), stat="identity") +
  geom_errorbar (position=position_dodge(width=0.9), width=0.2, colour="black") +
    facet_grid(~ Device) +
  labs(x = "", y = "FIT DUE [a.u.]", fill="") + 
    theme(legend.position="bottom")
  #theme(legend.position="bottom",axis.text.x=element_text(size=14) , axis.text.y=element_text(size=14) , text = element_text(size = 14))
  #filename = paste("./plots/FIT_SDC_", device, ".pdf", sep="")
  ggsave("./plots/FIT_DUE_APU.pdf", plot, width = 12, height = 7)
  plot
  

```

##### NVIDIAs
SDC
```{r}
   datPlot = subset(datNormalized, Device=="K20" | Device == "TitanV" | Device == "TitanX")

  dfm1 = melt(datPlot[, c('Code', 'Device', 'FIT_SDC_high_err', 'FIT_SDC_high')], id.vars = c(1, 2, 3))
  colnames(dfm1) = c("Code", "Device", "Error", "Neutron_Type", "FIT")
  dfm1$Neutron_Type = "High Energy"
  dfm2 = melt(datPlot[, c('Code', 'Device', 'FIT_SDC_thermals_err', 'FIT_SDC_thermals')], id.vars = c(1, 2, 3))
  colnames(dfm2) = c("Code", "Device", "Error", "Neutron_Type", "FIT")
  dfm2$Neutron_Type = "Thermals"
  dfm3 = melt(datPlot[, c('Code', 'Device', 'FIT_SDC_thermals_storm_err', 'FIT_SDC_thermals_storm')], id.vars = c(1, 2, 3))
  colnames(dfm3) = c("Code", "Device", "Error", "Neutron_Type", "FIT")
  dfm3$Neutron_Type = "Thermals (Storm)"
  dfm = rbind(dfm1, dfm2, dfm3)
  
  dfm$Device <- factor(dfm$Device, levels = c("K20", "TitanX", "TitanV"))
  
  plot = ggplot(dfm, aes(x=Code, weight=FIT, ymin=FIT-Error, ymax=FIT+Error, fill=Neutron_Type)) +
  geom_bar      (position=position_dodge(), aes(y=FIT), stat="identity") +
  geom_errorbar (position=position_dodge(width=0.9), width=0.2, colour="black") +
    facet_grid(~ Device) +
  labs(x = "", y = "FIT SDC [a.u.]", fill="") +
    theme(legend.position="bottom")
  #theme(legend.position="bottom",axis.text.x=element_text(size=14) , axis.text.y=element_text(size=14) , text = element_text(size = 14))
  #filename = paste("./plots/FIT_SDC_", device, ".pdf", sep="")
  ggsave("./plots/FIT_SDC_NVIDIA.pdf", plot, width = 12, height = 7)
  plot
  

```
DUE
```{r}
   datPlot = subset(datNormalized, Device=="K20" | Device == "TitanV" | Device == "TitanX")

  dfm1 = melt(datPlot[, c('Code', 'Device', 'FIT_DUE_high_err', 'FIT_DUE_high')], id.vars = c(1, 2, 3))
  colnames(dfm1) = c("Code", "Device", "Error", "Neutron_Type", "FIT")
  dfm1$Neutron_Type = "High Energy"
  dfm2 = melt(datPlot[, c('Code', 'Device', 'FIT_DUE_thermals_err', 'FIT_DUE_thermals')], id.vars = c(1, 2, 3))
  colnames(dfm2) = c("Code", "Device", "Error", "Neutron_Type", "FIT")
  dfm2$Neutron_Type = "Thermals"
  dfm3 = melt(datPlot[, c('Code', 'Device', 'FIT_DUE_thermals_storm_err', 'FIT_DUE_thermals_storm')], id.vars = c(1, 2, 3))
  colnames(dfm3) = c("Code", "Device", "Error", "Neutron_Type", "FIT")
  dfm3$Neutron_Type = "Thermals (Storm)"
  dfm = rbind(dfm1, dfm2, dfm3)
  
  dfm$Device <- factor(dfm$Device, levels = c("K20", "TitanX", "TitanV"))
  
  plot = ggplot(dfm, aes(x=Code, weight=FIT, ymin=FIT-Error, ymax=FIT+Error, fill=Neutron_Type)) +
  geom_bar      (position=position_dodge(), aes(y=FIT), stat="identity") +
  geom_errorbar (position=position_dodge(width=0.9), width=0.2, colour="black") +
    facet_grid(~ Device) +
  labs(x = "", y = "FIT DUE [a.u.]", fill="") +
    theme(legend.position="bottom")
  #theme(legend.position="bottom",axis.text.x=element_text(size=14) , axis.text.y=element_text(size=14) , text = element_text(size = 14))
  #filename = paste("./plots/FIT_SDC_", device, ".pdf", sep="")
  ggsave("./plots/FIT_DUE_NVIDIA.pdf", plot, width = 12, height = 7)
  plot
  

```

##### Xeon Phi
SDC
```{r}
fit_sdc_plot_errbars("XeonPhi")
```

DUE
```{r}
fit_due_plot_errbars("XeonPhi")
```



##### TitanX

SDC
```{r}
fit_sdc_plot_errbars("TitanX")
```

DUE
```{r}
fit_due_plot_errbars("TitanX")
```


##### TitanV
SDC
```{r}
fit_sdc_plot_errbars("TitanV")
```

DUE
```{r}
fit_due_plot_errbars("TitanV")
```


##### K20

SDC
```{r}
fit_sdc_plot_errbars("K20")
```

DUE
```{r}
fit_due_plot_errbars("K20")
```


##### CPU

SDC
```{r}
fit_sdc_plot_errbars("CPU")
```

DUE
```{r}
fit_due_plot_errbars("CPU")
```


##### GPUembedded

SDC
```{r}
fit_sdc_plot_errbars("GPUembedded")
```

DUE
```{r}
fit_due_plot_errbars("GPUembedded")
```



##### CPU+GPU

SDC
```{r}
fit_sdc_plot_errbars("CPU+GPU")
```

DUE
```{r}
fit_due_plot_errbars("CPU+GPU")
```

##### FPGA

SDC
```{r}
fit_sdc_plot_errbars("FPGA")
```
