---
title: "DSN2019 FIT"
author: "Daniel"
date: "December 1, 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading data and libraries

Load ggplot2 for plotting data and the CSV file with all data. We also correct the cross section of thermals since the rotax spectrum is different, which means we should correct the fluence we had before by a factor of (4.96/2.71). Thus, we divide the cross section by this factor since the cross section is (number of errors)/(fluence).

```{r}
library(ggplot2)
library(reshape2)

dat = read.csv("data_formatted.csv",sep=",")

dat$cross_section_SDC_thermals = dat$cross_section_SDC_thermals / (4.96/2.71)

summary(dat)
```


## Normalize SDC and DUE Cross Sections

Find the minimum value for each device and normalize SDC and DUE cross sections. Then, append the values normalize to a new data frame called "datNormalized"

```{r}
datNormalized = dat

normalizeCS <- function(df){
  tmp_values = c(df$cross_section_SDC_high, df$cross_section_DUE_high, df$cross_section_SDC_thermals, df$cross_section_DUE_thermals)
  tmp_values = tmp_values[tmp_values > 0] # remove zeros in case there is zeros
  tmp_min = min(tmp_values, na.rm=TRUE) # get the minimum cross section value
  for (board in unique(df$Device)){
    print(paste("Device: ", board, "; Minimum: ",tmp_min))
    datNormalized[datNormalized$Device == board, ]$cross_section_SDC_high = datNormalized[datNormalized$Device == board, ]$cross_section_SDC_high / tmp_min
    datNormalized[datNormalized$Device == board, ]$cross_section_DUE_high = datNormalized[datNormalized$Device == board, ]$cross_section_DUE_high / tmp_min
    datNormalized[datNormalized$Device == board, ]$cross_section_SDC_thermals = datNormalized[datNormalized$Device == board, ]$cross_section_SDC_thermals / tmp_min
    datNormalized[datNormalized$Device == board, ]$cross_section_DUE_thermals = datNormalized[datNormalized$Device == board, ]$cross_section_DUE_thermals / tmp_min
  }
  
  
}

AMD = c("CPU", "CPU+GPU", "GPUembedded")
NVIDIA = c("K20", "TitanX", "TitanV")

amd_df = dat[dat$Device %in% AMD, ]
#normalizeCS(amd_df)
  tmp_values = c(amd_df$cross_section_SDC_high, amd_df$cross_section_DUE_high, amd_df$cross_section_SDC_thermals, amd_df$cross_section_DUE_thermals)
  tmp_values = tmp_values[tmp_values > 0] # remove zeros in case there is zeros
  tmp_min = min(tmp_values, na.rm=TRUE) # get the minimum cross section value
  print(paste("Device: AMD Minimum: ",tmp_min))
  for (board in unique(amd_df$Device)){
    print(paste("Device: ", board, "; Minimum: ",tmp_min))
    datNormalized[datNormalized$Device == board, ]$cross_section_SDC_high = datNormalized[datNormalized$Device == board, ]$cross_section_SDC_high / tmp_min
    datNormalized[datNormalized$Device == board, ]$cross_section_DUE_high = datNormalized[datNormalized$Device == board, ]$cross_section_DUE_high / tmp_min
    datNormalized[datNormalized$Device == board, ]$cross_section_SDC_thermals = datNormalized[datNormalized$Device == board, ]$cross_section_SDC_thermals / tmp_min
    datNormalized[datNormalized$Device == board, ]$cross_section_DUE_thermals = datNormalized[datNormalized$Device == board, ]$cross_section_DUE_thermals / tmp_min
  }


nvidia_df = dat[dat$Device %in% NVIDIA, ]
#normalizeCS(nvidia_df)
  tmp_values = c(nvidia_df$cross_section_SDC_high, nvidia_df$cross_section_DUE_high, nvidia_df$cross_section_SDC_thermals, nvidia_df$cross_section_DUE_thermals)
  tmp_values = tmp_values[tmp_values > 0] # remove zeros in case there is zeros
  tmp_min = min(tmp_values, na.rm=TRUE) # get the minimum cross section value
  print(paste("Device: NVIDIA Minimum: ",tmp_min))
  for (board in unique(nvidia_df$Device)){
    print(paste("Device: ", board, "; Minimum: ",tmp_min))
    datNormalized[datNormalized$Device == board, ]$cross_section_SDC_high = datNormalized[datNormalized$Device == board, ]$cross_section_SDC_high / tmp_min
    datNormalized[datNormalized$Device == board, ]$cross_section_DUE_high = datNormalized[datNormalized$Device == board, ]$cross_section_DUE_high / tmp_min
    datNormalized[datNormalized$Device == board, ]$cross_section_SDC_thermals = datNormalized[datNormalized$Device == board, ]$cross_section_SDC_thermals / tmp_min
    datNormalized[datNormalized$Device == board, ]$cross_section_DUE_thermals = datNormalized[datNormalized$Device == board, ]$cross_section_DUE_thermals / tmp_min
  }
  
xeon_df = dat[dat$Device == "XeonPhi", ]
#normalizeCS(xeon_df)
  tmp_values = c(xeon_df$cross_section_SDC_high, xeon_df$cross_section_DUE_high, xeon_df$cross_section_SDC_thermals, xeon_df$cross_section_DUE_thermals)
  tmp_values = tmp_values[tmp_values > 0] # remove zeros in case there is zeros
  tmp_min = min(tmp_values, na.rm=TRUE) # get the minimum cross section value
  print(paste("Device: Xeon Minimum: ",tmp_min))
  for (board in unique(xeon_df$Device)){
    print(paste("Device: ", board, "; Minimum: ",tmp_min))
    datNormalized[datNormalized$Device == board, ]$cross_section_SDC_high = datNormalized[datNormalized$Device == board, ]$cross_section_SDC_high / tmp_min
    datNormalized[datNormalized$Device == board, ]$cross_section_DUE_high = datNormalized[datNormalized$Device == board, ]$cross_section_DUE_high / tmp_min
    datNormalized[datNormalized$Device == board, ]$cross_section_SDC_thermals = datNormalized[datNormalized$Device == board, ]$cross_section_SDC_thermals / tmp_min
    datNormalized[datNormalized$Device == board, ]$cross_section_DUE_thermals = datNormalized[datNormalized$Device == board, ]$cross_section_DUE_thermals / tmp_min
  }
  
fpga_df = dat[dat$Device == "FPGA", ]
#normalizeCS(fpga_df)
  tmp_values = c(fpga_df$cross_section_SDC_high, fpga_df$cross_section_DUE_high, fpga_df$cross_section_SDC_thermals, fpga_df$cross_section_DUE_thermals)
  tmp_values = tmp_values[tmp_values > 0] # remove zeros in case there is zeros
  tmp_min = min(tmp_values, na.rm=TRUE) # get the minimum cross section value
  print(paste("Device: FPGA Minimum: ",tmp_min))
  for (board in unique(fpga_df$Device)){
    print(paste("Device: ", board, "; Minimum: ",tmp_min))
    datNormalized[datNormalized$Device == board, ]$cross_section_SDC_high = datNormalized[datNormalized$Device == board, ]$cross_section_SDC_high / tmp_min
    datNormalized[datNormalized$Device == board, ]$cross_section_DUE_high = datNormalized[datNormalized$Device == board, ]$cross_section_DUE_high / tmp_min
    datNormalized[datNormalized$Device == board, ]$cross_section_SDC_thermals = datNormalized[datNormalized$Device == board, ]$cross_section_SDC_thermals / tmp_min
    datNormalized[datNormalized$Device == board, ]$cross_section_DUE_thermals = datNormalized[datNormalized$Device == board, ]$cross_section_DUE_thermals / tmp_min
  }
  


datNormalized$SDC_DUE_ratio_high = datNormalized$cross_section_DUE_high / datNormalized$cross_section_SDC_high

datNormalized$SDC_DUE_ratio_thermal = datNormalized$cross_section_DUE_thermals / datNormalized$cross_section_SDC_thermals
#for (board in unique(dat$Device)) {
#  # Get all cross section values for one device
#  tmp_values = c(subset(dat,dat$Device==board)$cross_section_SDC_high, subset(dat,dat$Device==board)$cross_section_DUE_high, subset(dat,dat$Device==board)$cross_section_SDC_thermals, subset(dat,dat$Device==board)$cross_section_DUE_thermals)
#  tmp_values = tmp_values[tmp_values > 0] # remove zeros in case there is zeros
#  tmp_min = min(tmp_values, na.rm=TRUE) # get the minimum cross section value
#  print(paste("Device: ", board, "; Minimum: ",tmp_min))
  
#  # Normalize all date from one device to the minimum value found
#  datNormalized[datNormalized$Device == board, ]$cross_section_SDC_high = datNormalized[datNormalized$Device == board, ]$cross_section_SDC_high / tmp_min
#  datNormalized[datNormalized$Device == board, ]$cross_section_DUE_high = datNormalized[datNormalized$Device == board, ]$cross_section_DUE_high / tmp_min
#  datNormalized[datNormalized$Device == board, ]$cross_section_SDC_thermals = datNormalized[datNormalized$Device == board, ]$cross_section_SDC_thermals / tmp_min
#  datNormalized[datNormalized$Device == board, ]$cross_section_DUE_thermals = datNormalized[datNormalized$Device == board, ]$cross_section_DUE_thermals / tmp_min
#}
```


## Compute FIT for High Energy

Normal flux is 13 neutrons per cm^2 per hour. Since data is normalized, there is no need to multiply by 10^9
Flux inside a supercomputer hall is 31.65, and flux for an airplane at 35,000 feet is 4582.63

```{r}
datNormalized$FIT_SDC_high = datNormalized$cross_section_SDC_high * 13
datNormalized$FIT_DUE_high = datNormalized$cross_section_DUE_high * 13

datNormalized$FIT_SDC_high_LANLsupercomputer = datNormalized$cross_section_SDC_high * 31.65
datNormalized$FIT_DUE_high_LANLsupercomputer = datNormalized$cross_section_DUE_high * 31.65

datNormalized$FIT_SDC_high_ORNLsupercomputer = datNormalized$cross_section_SDC_high * 7.12173913
datNormalized$FIT_DUE_high_ORNLsupercomputer = datNormalized$cross_section_DUE_high * 7.12173913

datNormalized$FIT_SDC_high_airplane = datNormalized$cross_section_SDC_high * 4582.63
datNormalized$FIT_DUE_high_airplane = datNormalized$cross_section_DUE_high * 4582.63
```

## Compute FIT for Thermals


Normal flux is 4 neutrons per cm^2 per hour under normal environments. 

```{r}
datNormalized$FIT_SDC_thermals = datNormalized$cross_section_SDC_thermals * 4
datNormalized$FIT_DUE_thermals = datNormalized$cross_section_DUE_thermals * 4
```

During a thunderstrom the neutron flux is about 8 neutrons

```{r}
datNormalized$FIT_SDC_thermals_storm = datNormalized$cross_section_SDC_thermals * 8
datNormalized$FIT_DUE_thermals_storm = datNormalized$cross_section_DUE_thermals * 8
```

LANL Supercomputer hall thermal flux is 14 neutrons per cm^2 per hour

```{r}
datNormalized$FIT_SDC_thermals_LANLsupercomputer = datNormalized$cross_section_SDC_thermals * 14
datNormalized$FIT_DUE_thermals_LANLsupercomputer = datNormalized$cross_section_DUE_thermals * 14
```

ORNL Supercomputer hall thermal flux is 14 neutrons per cm^2 per hour

```{r}
datNormalized$FIT_SDC_thermals_ORNLsupercomputer = datNormalized$cross_section_SDC_thermals * 3.15
datNormalized$FIT_DUE_thermals_ORNLsupercomputer = datNormalized$cross_section_DUE_thermals * 3.15
```

Airplane at 35,000 feet thermal flux is 1410.04 neutrons per cm^2 per hour
```{r}
datNormalized$FIT_SDC_thermals_airplane = datNormalized$cross_section_SDC_thermals * 1410.04
datNormalized$FIT_DUE_thermals_airplane = datNormalized$cross_section_DUE_thermals * 1410.04
```


## Compute the error bars

Using the Poisson distribution with 95% confidence, which is  1.96*sqrt(test_mean/#tests)

```{r}
  datNormalized$cross_section_SDC_high_err = 1.96*sqrt(datNormalized$cross_section_SDC_high/datNormalized$number_SDCs_high)
  datNormalized$cross_section_DUE_high_err = 1.96*sqrt(datNormalized$cross_section_DUE_high/datNormalized$number_DUE_high)

  datNormalized$cross_section_SDC_thermals_err = 1.96*sqrt(datNormalized$cross_section_SDC_thermals/datNormalized$number_SDCs_thermals)
  datNormalized$cross_section_DUE_thermals_err = 1.96*sqrt(datNormalized$cross_section_DUE_thermals/datNormalized$number_DUE_thermals)
  
  datNormalized$FIT_SDC_high_err = 1.96*sqrt(datNormalized$FIT_SDC_high/datNormalized$number_SDCs_high)
  datNormalized$FIT_DUE_high_err = 1.96*sqrt(datNormalized$FIT_DUE_high/datNormalized$number_DUE_high)
  
  datNormalized$FIT_SDC_high_LANLsupercomputer_err = 1.96*sqrt(datNormalized$FIT_SDC_high_LANLsupercomputer/datNormalized$number_SDCs_high)
  datNormalized$FIT_DUE_high_LANLsupercomputer_err = 1.96*sqrt(datNormalized$FIT_DUE_high_LANLsupercomputer/datNormalized$number_DUE_high)
  
  datNormalized$FIT_SDC_high_ORNLsupercomputer_err = 1.96*sqrt(datNormalized$FIT_SDC_high_ORNLsupercomputer/datNormalized$number_SDCs_high)
  datNormalized$FIT_DUE_high_ORNLsupercomputer_err = 1.96*sqrt(datNormalized$FIT_DUE_high_ORNLsupercomputer/datNormalized$number_DUE_high)
  
  datNormalized$FIT_SDC_high_airplane_err = 1.96*sqrt(datNormalized$FIT_SDC_high_airplane/datNormalized$number_SDCs_high)
  datNormalized$FIT_DUE_high_airplane_err = 1.96*sqrt(datNormalized$FIT_DUE_high_airplane/datNormalized$number_DUE_high)

  datNormalized$FIT_DUE_thermals_err = 1.96*sqrt(datNormalized$FIT_DUE_thermals/datNormalized$number_DUE_thermals)
  datNormalized$FIT_SDC_thermals_err = 1.96*sqrt(datNormalized$FIT_SDC_thermals/datNormalized$number_SDCs_thermals)

  datNormalized$FIT_SDC_thermals_storm_err = 1.96*sqrt(datNormalized$FIT_SDC_thermals_storm/datNormalized$number_SDCs_thermals)
  datNormalized$FIT_DUE_thermals_storm_err = 1.96*sqrt(datNormalized$FIT_DUE_thermals_storm/datNormalized$number_DUE_thermals)
  
  datNormalized$FIT_DUE_thermals_airplane_err = 1.96*sqrt(datNormalized$FIT_DUE_thermals_airplane/datNormalized$number_DUE_thermals)
  datNormalized$FIT_SDC_thermals_airplane_err = 1.96*sqrt(datNormalized$FIT_SDC_thermals_airplane/datNormalized$number_SDCs_thermals)
  
  datNormalized$FIT_DUE_thermals_ORNLsupercomputer_err = 1.96*sqrt(datNormalized$FIT_DUE_thermals_ORNLsupercomputer/datNormalized$number_DUE_thermals)
  datNormalized$FIT_SDC_thermals_ORNLsupercomputer_err = 1.96*sqrt(datNormalized$FIT_SDC_thermals_ORNLsupercomputer/datNormalized$number_SDCs_thermals)
  
  datNormalized$FIT_DUE_thermals_LANLsupercomputer_err = 1.96*sqrt(datNormalized$FIT_DUE_thermals_LANLsupercomputer/datNormalized$number_DUE_thermals)
  datNormalized$FIT_SDC_thermals_LANLsupercomputer_err = 1.96*sqrt(datNormalized$FIT_SDC_thermals_LANLsupercomputer/datNormalized$number_SDCs_thermals)
  
  write.csv(datNormalized, file="~/DSN.csv")
```



## FIT Plots

### AMD

```{r}
  datPlot = subset(datNormalized, Device=="CPU" | Device == "GPUembedded" | Device == "CPU+GPU")

  #SDC
  dfm1 = melt(datPlot[, c('Code', 'Device', 'FIT_SDC_high_err', 'FIT_SDC_high')], id.vars = c(1, 2, 3))
  colnames(dfm1) = c("Code", "Device", "Error", "Neutron_Type", "FIT")
  dfm1$Neutron_Type = "High Energy"
  dfm2 = melt(datPlot[, c('Code', 'Device', 'FIT_SDC_thermals_err', 'FIT_SDC_thermals')], id.vars = c(1, 2, 3))
  colnames(dfm2) = c("Code", "Device", "Error", "Neutron_Type", "FIT")
  dfm2$Neutron_Type = "Thermals"
  dfm3 = melt(datPlot[, c('Code', 'Device', 'FIT_SDC_thermals_storm_err', 'FIT_SDC_thermals_storm')], id.vars = c(1, 2, 3))
  colnames(dfm3) = c("Code", "Device", "Error", "Neutron_Type", "FIT")
  dfm3$Neutron_Type = "Thermals (Storm)"
  dfm = rbind(dfm1, dfm2, dfm3)
  
  dfm[2] <- data.frame(lapply(dfm[2], function(x) { gsub("GPUembedded", "AMD\nGPU", x) }))
  dfm[2] <- data.frame(lapply(dfm[2], function(x) { gsub("CPU", "AMD\nCPU", x) }))
  dfm[2] <- data.frame(lapply(dfm[2], function(x) { gsub("CPU+GPU", "AMD\nCPU+GPU", x) }))
  
  dfm$Event_Type = "SDC"
  
  #DUE
  dfm4 = melt(datPlot[, c('Code', 'Device', 'FIT_DUE_high_err', 'FIT_DUE_high')], id.vars = c(1, 2, 3))
  colnames(dfm4) = c("Code", "Device", "Error", "Neutron_Type", "FIT")
  dfm4$Neutron_Type = "High Energy"
  dfm5 = melt(datPlot[, c('Code', 'Device', 'FIT_DUE_thermals_err', 'FIT_DUE_thermals')], id.vars = c(1, 2, 3))
  colnames(dfm5) = c("Code", "Device", "Error", "Neutron_Type", "FIT")
  dfm5$Neutron_Type = "Thermals"
  dfm6 = melt(datPlot[, c('Code', 'Device', 'FIT_DUE_thermals_storm_err', 'FIT_DUE_thermals_storm')], id.vars = c(1, 2, 3))
  colnames(dfm6) = c("Code", "Device", "Error", "Neutron_Type", "FIT")
  dfm6$Neutron_Type = "Thermals (Storm)"
  dfmD = rbind(dfm4, dfm5, dfm6)
  
  dfmD[2] <- data.frame(lapply(dfmD[2], function(x) { gsub("GPUembedded", "AMD\nGPU", x) }))
  dfmD[2] <- data.frame(lapply(dfmD[2], function(x) { gsub("CPU", "AMD\nCPU", x) }))
  dfmD[2] <- data.frame(lapply(dfmD[2], function(x) { gsub("CPU+GPU", "AMD\nCPU+GPU", x) }))
  
  dfmD$Event_Type = "DUE"

  dfm = rbind(dfm, dfmD)
  
  # changing factor order
  dfm$Device <- factor(dfm$Device, levels = c("AMD\nCPU", "AMD\nGPU", "AMD\nCPU+GPU"))
  
  
  plot = ggplot(dfm, aes(x=Code, weight=FIT, ymin=FIT-Error, ymax=FIT+Error, fill=Neutron_Type)) +
  geom_bar      (position=position_dodge(), aes(y=FIT), stat="identity") +
  geom_errorbar (position=position_dodge(width=0.9), width=0.2, colour="black") +
    facet_grid(Event_Type ~ Device, scale="free") +
  labs(x = "", y = "FIT [a.u.]", fill="") + 
    scale_fill_manual(values=c("#33a02c", "#a6cee3", "#1f78b4")) +
    theme(legend.position="bottom")
  #theme(legend.position="bottom",axis.text.x=element_text(size=14) , axis.text.y=element_text(size=14) , text = element_text(size = 14))
  ggsave("./plots_final/FIT_SDC_DUE_APU.pdf", plot, width = 12, height = 7)
  plot
  

```

### NVIDIA

```{r}
  datPlot = subset(datNormalized, Device=="K20" | Device == "TitanV" | Device == "TitanX")

  #SDC
  dfm1 = melt(datPlot[, c('Code', 'Device', 'FIT_SDC_high_err', 'FIT_SDC_high')], id.vars = c(1, 2, 3))
  colnames(dfm1) = c("Code", "Device", "Error", "Neutron_Type", "FIT")
  dfm1$Neutron_Type = "High Energy"
  dfm2 = melt(datPlot[, c('Code', 'Device', 'FIT_SDC_thermals_err', 'FIT_SDC_thermals')], id.vars = c(1, 2, 3))
  colnames(dfm2) = c("Code", "Device", "Error", "Neutron_Type", "FIT")
  dfm2$Neutron_Type = "Thermals"
  dfm3 = melt(datPlot[, c('Code', 'Device', 'FIT_SDC_thermals_storm_err', 'FIT_SDC_thermals_storm')], id.vars = c(1, 2, 3))
  colnames(dfm3) = c("Code", "Device", "Error", "Neutron_Type", "FIT")
  dfm3$Neutron_Type = "Thermals (Storm)"
  dfm = rbind(dfm1, dfm2, dfm3)
  
  dfm$Event_Type = "SDC"
  
  #DUE
  dfm4 = melt(datPlot[, c('Code', 'Device', 'FIT_DUE_high_err', 'FIT_DUE_high')], id.vars = c(1, 2, 3))
  colnames(dfm4) = c("Code", "Device", "Error", "Neutron_Type", "FIT")
  dfm4$Neutron_Type = "High Energy"
  dfm5 = melt(datPlot[, c('Code', 'Device', 'FIT_DUE_thermals_err', 'FIT_DUE_thermals')], id.vars = c(1, 2, 3))
  colnames(dfm5) = c("Code", "Device", "Error", "Neutron_Type", "FIT")
  dfm5$Neutron_Type = "Thermals"
  dfm6 = melt(datPlot[, c('Code', 'Device', 'FIT_DUE_thermals_storm_err', 'FIT_DUE_thermals_storm')], id.vars = c(1, 2, 3))
  colnames(dfm6) = c("Code", "Device", "Error", "Neutron_Type", "FIT")
  dfm6$Neutron_Type = "Thermals (Storm)"
  dfmD = rbind(dfm4, dfm5, dfm6)

  dfmD$Event_Type = "DUE"

  dfm = rbind(dfm, dfmD)
  
  # changing factor order
  dfm$Device <- factor(dfm$Device, levels = c("K20", "TitanX", "TitanV"))
  
  
  plot = ggplot(dfm, aes(x=Code, weight=FIT, ymin=FIT-Error, ymax=FIT+Error, fill=Neutron_Type)) +
  geom_bar      (position=position_dodge(), aes(y=FIT), stat="identity") +
  geom_errorbar (position=position_dodge(width=0.9), width=0.2, colour="black") +
    facet_grid(Event_Type ~ Device, scale="free") +
  labs(x = "", y = "FIT [a.u.]", fill="") + 
    scale_fill_manual(values=c("#33a02c", "#a6cee3", "#1f78b4")) +
    theme(legend.position="bottom")
  #theme(legend.position="bottom",axis.text.x=element_text(size=14) , axis.text.y=element_text(size=14) , text = element_text(size = 14))
  ggsave("./plots_final/FIT_SDC_DUE_NVIDIA.pdf", plot, width = 12, height = 7)
  plot

```


### Xeon Phi

```{r}
  datPlot = subset(datNormalized, Device=="XeonPhi")

  #SDC
  dfm1 = melt(datPlot[, c('Code', 'Device', 'FIT_SDC_high_err', 'FIT_SDC_high')], id.vars = c(1, 2, 3))
  colnames(dfm1) = c("Code", "Device", "Error", "Neutron_Type", "FIT")
  dfm1$Neutron_Type = "High Energy"
  dfm2 = melt(datPlot[, c('Code', 'Device', 'FIT_SDC_thermals_err', 'FIT_SDC_thermals')], id.vars = c(1, 2, 3))
  colnames(dfm2) = c("Code", "Device", "Error", "Neutron_Type", "FIT")
  dfm2$Neutron_Type = "Thermals"
  dfm3 = melt(datPlot[, c('Code', 'Device', 'FIT_SDC_thermals_storm_err', 'FIT_SDC_thermals_storm')], id.vars = c(1, 2, 3))
  colnames(dfm3) = c("Code", "Device", "Error", "Neutron_Type", "FIT")
  dfm3$Neutron_Type = "Thermals (Storm)"
  dfm = rbind(dfm1, dfm2, dfm3)
  
  dfm$Event_Type = "SDC"
  
  #DUE
  dfm4 = melt(datPlot[, c('Code', 'Device', 'FIT_DUE_high_err', 'FIT_DUE_high')], id.vars = c(1, 2, 3))
  colnames(dfm4) = c("Code", "Device", "Error", "Neutron_Type", "FIT")
  dfm4$Neutron_Type = "High Energy"
  dfm5 = melt(datPlot[, c('Code', 'Device', 'FIT_DUE_thermals_err', 'FIT_DUE_thermals')], id.vars = c(1, 2, 3))
  colnames(dfm5) = c("Code", "Device", "Error", "Neutron_Type", "FIT")
  dfm5$Neutron_Type = "Thermals"
  dfm6 = melt(datPlot[, c('Code', 'Device', 'FIT_DUE_thermals_storm_err', 'FIT_DUE_thermals_storm')], id.vars = c(1, 2, 3))
  colnames(dfm6) = c("Code", "Device", "Error", "Neutron_Type", "FIT")
  dfm6$Neutron_Type = "Thermals (Storm)"
  dfmD = rbind(dfm4, dfm5, dfm6)

  dfmD$Event_Type = "DUE"

  dfm = rbind(dfm, dfmD)
  
  # changing factor order
  #dfm$Device <- factor(dfm$Device, levels = c("K20", "TitanX", "TitanV"))
  
  
  plot = ggplot(dfm, aes(x=Code, weight=FIT, ymin=FIT-Error, ymax=FIT+Error, fill=Neutron_Type)) +
  geom_bar      (position=position_dodge(), aes(y=FIT), stat="identity") +
  geom_errorbar (position=position_dodge(width=0.9), width=0.2, colour="black") +
    facet_grid(Event_Type ~ ., scale="free") +
  labs(x = "", y = "FIT [a.u.]", fill="") + 
    scale_fill_manual(values=c("#33a02c", "#a6cee3", "#1f78b4")) +
    theme(legend.position="bottom")
  #theme(legend.position="bottom",axis.text.x=element_text(size=14) , axis.text.y=element_text(size=14) , text = element_text(size = 14))
  ggsave("./plots_final/FIT_SDC_DUE_XeonPhi.pdf", plot, width = 5, height = 6)
  plot

```


### FPGA

```{r}
  datPlot = subset(datNormalized, Device=="FPGA")

  #SDC
  dfm1 = melt(datPlot[, c('Code', 'Device', 'FIT_SDC_high_err', 'FIT_SDC_high')], id.vars = c(1, 2, 3))
  colnames(dfm1) = c("Code", "Device", "Error", "Neutron_Type", "FIT")
  dfm1$Neutron_Type = "High Energy"
  dfm2 = melt(datPlot[, c('Code', 'Device', 'FIT_SDC_thermals_err', 'FIT_SDC_thermals')], id.vars = c(1, 2, 3))
  colnames(dfm2) = c("Code", "Device", "Error", "Neutron_Type", "FIT")
  dfm2$Neutron_Type = "Thermals"
  dfm3 = melt(datPlot[, c('Code', 'Device', 'FIT_SDC_thermals_storm_err', 'FIT_SDC_thermals_storm')], id.vars = c(1, 2, 3))
  colnames(dfm3) = c("Code", "Device", "Error", "Neutron_Type", "FIT")
  dfm3$Neutron_Type = "Thermals (Storm)"
  dfm = rbind(dfm1, dfm2, dfm3)
  
  dfm$Event_Type = "SDC"
  

  #dfm = rbind(dfm, dfmD)
  
  # changing factor order
  #dfm$Device <- factor(dfm$Device, levels = c("K20", "TitanX", "TitanV"))
  
  
  plot = ggplot(dfm, aes(x=Code, weight=FIT, ymin=FIT-Error, ymax=FIT+Error, fill=Neutron_Type)) +
  geom_bar      (position=position_dodge(), aes(y=FIT), stat="identity") +
  geom_errorbar (position=position_dodge(width=0.9), width=0.2, colour="black") +
    #facet_grid(Event_Type ~ ., scale="free") +
  labs(x = "", y = "FIT SDC [a.u.]", fill="") + 
    scale_fill_manual(values=c("#33a02c", "#a6cee3", "#1f78b4")) +
    theme(legend.position="bottom")
  #theme(legend.position="bottom",axis.text.x=element_text(size=14) , axis.text.y=element_text(size=14) , text = element_text(size = 14))
  ggsave("./plots_final/FIT_SDC_DUE_FPGA.pdf", plot, width = 5, height = 5)
  plot

```
