---
title: "DSN 2019 Cross Sections"
author: "Daniel"
date: "April 04, 2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading data and libraries

Load ggplot2 for plotting data and the CSV file with all data. We also correct the cross section of thermals since the rotax spectrum is different, which means we should correct the fluence we had before by a factor of (4.96/2.71). Thus, we divide the cross section by this factor since the cross section is (number of errors)/(fluence).

```{r}
library(ggplot2)
library(reshape2)

dat = read.csv("data_formatted.csv",sep=",")

dat$cross_section_SDC_thermals = dat$cross_section_SDC_thermals / (4.96/2.71)

summary(dat)
```


## Normalize SDC and DUE Cross Sections

Find the minimum value for each device and normalize SDC and DUE cross sections. Then, append the values normalize to a new data frame called "datNormalized"

```{r}
datNormalized = dat
for (board in unique(dat$Device)) {
  # Get all cross section values for one device
  tmp_values = c(subset(dat,dat$Device==board)$cross_section_SDC_high, subset(dat,dat$Device==board)$cross_section_DUE_high, subset(dat,dat$Device==board)$cross_section_SDC_thermals, subset(dat,dat$Device==board)$cross_section_DUE_thermals)
  tmp_values = tmp_values[tmp_values > 0] # remove zeros in case there is zeros
  tmp_min = min(tmp_values, na.rm=TRUE) # get the minimum cross section value
  print(paste("Device: ", board, "; Minimum: ",tmp_min))
  
  # Normalize all date from one device to the minimum value found
  datNormalized[datNormalized$Device == board, ]$cross_section_SDC_high = datNormalized[datNormalized$Device == board, ]$cross_section_SDC_high / tmp_min
  datNormalized[datNormalized$Device == board, ]$cross_section_DUE_high = datNormalized[datNormalized$Device == board, ]$cross_section_DUE_high / tmp_min
  datNormalized[datNormalized$Device == board, ]$cross_section_SDC_thermals = datNormalized[datNormalized$Device == board, ]$cross_section_SDC_thermals / tmp_min
  datNormalized[datNormalized$Device == board, ]$cross_section_DUE_thermals = datNormalized[datNormalized$Device == board, ]$cross_section_DUE_thermals / tmp_min
}

```

## Calculate the average cross section per device

```{r}
dat_mean = aggregate(datNormalized[, c('cross_section_SDC_high', 'cross_section_DUE_high', 'cross_section_SDC_thermals', 'cross_section_DUE_thermals')], list(datNormalized$Device), mean, na.rm=TRUE,na.action = na.omit)
#dat_mean
```


## Compute FIT rates for some scenarios, percentage
High Energy scenarios:
sea level 13
Leadville 12.8X the sea leval = 12.8 * 13 = 166.4
Thermal flux scenarions:
place: <nominal>, <20% increase>, <44.4%>, <100% increase, rainy day>
sea level: 4, 4.8, 5.776, 8
Leadville 87, 104, 125.628, 174


```{r}

rm(dat_melted)
high = dat_mean$cross_section_SDC_high * 13
thermals = dat_mean$cross_section_SDC_thermals * 5.776
dat_mean$High_Energy = high*100/(high+thermals)
dat_mean$Thermals = thermals*100/(high+thermals)
dat_melted = melt(dat_mean[,c('Group.1', 'High_Energy', 'Thermals')], id.vars = 'Group.1' )
dat_melted$scenario = 'NSDC'
#dat_melted$scenario = 'NYC SDC'
#dat_melted = rbind(dat_melted, dat_melted2)

rm(dat_melted2)
high = dat_mean$cross_section_DUE_high * 13
thermals = dat_mean$cross_section_DUE_thermals * 5.776
dat_mean$High_Energy = high*100/(high+thermals)
dat_mean$Thermals = thermals*100/(high+thermals)
dat_melted2 = melt(dat_mean[,c('Group.1', 'High_Energy', 'Thermals')], id.vars = 'Group.1' )
dat_melted2$scenario = 'NDUE'
#dat_melted2$scenario = 'NYC DUE'
dat_melted = rbind(dat_melted, dat_melted2)


rm(dat_melted2)
high = dat_mean$cross_section_SDC_high * 166.4
thermals = dat_mean$cross_section_SDC_thermals * 125.628
dat_mean$High_Energy = high*100/(high+thermals)
dat_mean$Thermals = thermals*100/(high+thermals)
dat_melted2 = melt(dat_mean[,c('Group.1', 'High_Energy', 'Thermals')], id.vars = 'Group.1' )
dat_melted2$scenario = 'LSDC'
#dat_melted2$scenario = 'LXV SDC'
dat_melted = rbind(dat_melted, dat_melted2)

rm(dat_melted2)
high = dat_mean$cross_section_DUE_high * 166.4
thermals = dat_mean$cross_section_DUE_thermals * 125.628
dat_mean$High_Energy = high*100/(high+thermals)
dat_mean$Thermals = thermals*100/(high+thermals)
dat_melted2 = melt(dat_mean[,c('Group.1', 'High_Energy', 'Thermals')], id.vars = 'Group.1' )
dat_melted2$scenario = 'LDUE'
#dat_melted2$scenario = 'LXV DUE'
dat_melted = rbind(dat_melted, dat_melted2)

dat_melted$variable <- factor(dat_melted$variable, levels = c("Thermals", "High_Energy"))

dat_melted$scenario <- factor(dat_melted$scenario, levels = c("NSDC", "NDUE", "LSDC", "LDUE"))
#dat_melted$scenario <- factor(dat_melted$scenario, levels = c("NYC SDC", "NYC DUE", "LXV SDC", "LXV DUE"))
#dat_melted$scenario <- factor(dat_melted$scenario, levels = c("NYC SDC", "NYC DUE", "Leadville  SDC", "Leadville DUE"))

dat_melted$Group.1 <- factor(dat_melted$Group.1, levels = c( "CPU", "GPUembedded", "CPU+GPU", "XeonPhi", "K20", "TitanX", "TitanV", "FPGA"))

#dat_melted = dat_melted[which(dat_melted$Group.1 != "CPU" & dat_melted$Group.1 != "GPUembedded"),]

p = ggplot(dat_melted) +
  geom_bar(stat="identity",aes(x = scenario, y = value, fill=variable), position=position_stack()) +
  labs(x = "Location", y = "Average FIT Rate Contribution [%]") +
  #facet_wrap(~Group.1, scales = "free_y") +
  facet_wrap(~Group.1, ncol=4) +
  #scale_y_log10() +
  scale_fill_manual(values=c(
  "#0070c0"
  , "#c00000")
    , labels = c('Thermal', 'High Energy')
  )+
  theme(legend.title = element_blank(), legend.position="bottom",axis.text.x=element_text(size=13) , axis.text.y=element_text(size=14) , text = element_text(size = 14))

p
ggsave(p, file="SDC-scenarios-per.pdf", width = 12, height = 7)

```



